On particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2021-02-24 AvdMomZvolA_examples/ips_examples.tex
[AMZAE] Drafts of the intro

@@

\begin{figure}[h!]
%\center{\includegraphics[width=1\linewidth]{picture_12.pdf}}
\parbox{1\linewidth}{\caption{IPS of cardinality 10 and diameter 56}
\label{picture_12.pdf}}
\end{figure}

\begin{figure}[h!]
%\center{\includegraphics[width=1\linewidth]{picture_1260_R3.pdf}}
\parbox{1\linewidth}{\caption{IPS of cardinality 13 and diameter 1260}
\label{picture_1260_R3.pdf}}
\end{figure}

@@

\item
$\mathcal{P}=\sqrt{3}/{2} * \{ (\pm 56, 0),
(14, 0),
(-34, 0),
(-10, 24),
(-21 , 35),
(35, -21)\}
$
(Figure~\ref{picture_56.png}),

where $n = 7$, $\operatorname{diam(\mathcal{P})} = 56$. Using the ``blowing up''
construction, we obtain
\begin{equation}\label{result2}
d(m, 3m + 1) \leq 56
\end{equation}
The resulting estimate improves the estimate for $d(m, 3m)$, which is presented
in \cite{kemnitz1988punktmengen}. Figure~\ref{picture_12.pdf} shows an example
for $m = 3$.

\item
$\mathcal{P}=\sqrt{39}/{8} * \{ (\pm 5040, 0),
(1911, 315),
(2352, 0),
(944, 0),
(336, 0),
(2940, -420),
(2044, 220),
$

$
(735, 1155)\}
$
(Figure~\ref{picture_1260.png}),

where $n = 9$, $\operatorname{diam(\mathcal{P})} = 1260$. Using the ``blowing up''
construction, we obtain
\begin{equation}\label{result3}
d(m, 4m + 1) \leq 1260
\end{equation}
Figure~\ref{picture_1260_R3.pdf} shows an example for $m = 3$.

>>>>

The main purpose of this work is to provide examples of planar integral point sets
that may give the clue for development of further classification.

It's notable that any of the examples that are discussed below
is located on a union of at most three straight lines.
In the most pictures these lines are shown as solid lines.
For classification of planar IPS that are located on a union of two straight lines,
we refer the reader to~\cite{avdeev2019particular}.

There are some examples of planar IPS that are not contained in the union of any three straight lines:
for examples, these are heptagons presented in~\cite{kreisel2008heptagon} and 7-clusters from~\cite{kurz2013constructing}.
However, we have to keep in mind that the circular inversion under certain conditions
translates an integral point set into an integral point set
(although sometimes additional dilation is necessary).
On the other hand, the circular inversion may translate a straight line into a circle and vice versa.

Thus, we can consider \emph{generalized circles}, that are circles or straight lines;
obviously, in that point of view all the examples from~\cite{kreisel2008heptagon} and~\cite{kurz2013constructing}
are located on a union of three generalized circles,
because each seven points are located on a union of a circle and two straight lines.

@@

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/42_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 42 and diameter 2473117504}
\label{42_symm.png}}
\end{figure}

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/46_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 46 and diameter 3118278592}
\label{46_symm.png}}
\end{figure}

\begin{figure}[h!]
center{\includegraphics[width=1\linewidth]{./img/48_symm.png}}
\parbox{1\linewidth}{\caption{IPS of cardinality 48 and diameter 71720407616}
\label{48_symm.png}}
\end{figure}

@@

\item
$\mathcal{P}=\sqrt{154}/{1} * \{ (\pm 345596160; 0);
(\pm219513840 -15069600);
(\pm260201760; 0);
(\pm225792840; 0);
(\pm213234840; 0);
(\pm153961080; 0);
(\pm144668160; 0
(\pm25116000; 0);
(\pm694026840; 0);
(\pm514710560; 0);
(\pm359116940; 0);
(\pm13423904; 0);
(\pm75682880; 0);
(\pm464143680; 0);
(\pm827069880; 0);
(\pm92144325; 0);
(\pm1195180740; 0);
(\pm1236558752; 0);
(\pm44590560; 0);
(\pm339925740; 0);
(\pm117312468; 0)\}
$
(Figure~\ref{42_symm.png}),

where $n = 42$, $\operatorname{diam(\mathcal{P})} = 2473117504$. Using the ``blowing up''
construction, we obtain
\begin{equation}\label{result2}
d(m, 3m + 1) \leq 56
\end{equation}
The resulting estimate improves the estimate for $d(m, 3m)$, which is presented
in \cite{kemnitz1988punktmengen}. Figure~\ref{picture_12.pdf} shows an example
for $m = 3$.

\item
$\mathcal{P}=\sqrt{154}/{1} * \{ (\pm435751680; 0);
(\pm276778320; -19000800);
(\pm328080480; 0);
(\pm284695320; 0);
(\pm268861320; 0);
(\pm194124840; 0);
(\pm182407680; 0);
(\pm31668000; 0);
(\pm1559139296; 0);
(\pm1506967020; 0);
(\pm1042827240; 0);
(\pm875077320; 0);
(\pm648982880; 0);
(\pm585224640; 0);
(\pm452799620; 0);
(\pm95426240; 0);
(\pm16925792; 0);
(\pm116181975; 0);
(\pm428602020; 0);
(\pm56222880; 0);
(\pm769560480; 0);
(\pm626458560; 0);
(\pm130761918; 0)\}
$
(Figure~\ref{46_symm.png}),

where $n = 46$, $\operatorname{diam(\mathcal{P})} = 3118278592$. Using the ``blowing up''
construction, we obtain
\begin{equation}\label{result3}
d(m, 4m + 1) \leq 1260
\end{equation}
Figure~\ref{picture_1260_R3.pdf} shows an example for $m = 3$.

\item
$\mathcal{P}=\sqrt{154}/{1} * \{ (\pm10022288640; 0);
( \pm6365901360 ; -437018400); 
( \pm7545851040 ; 0); 
( \pm6547992360 ; 0); 
( \pm6183810360 ; 0); 
( \pm4464871320 ; 0); 
( \pm4195376640 ; 0); 
( \pm728364000 ; 0); 
( \pm35860203808 ; 0); 
( \pm34660241460 ; 0); 
( \pm23985026520 ; 0); 
( \pm20126778360 ; 0); 
( \pm14926606240 ; 0); 
( \pm13460166720 ; 0); 
( \pm10414391260 ; 0); 
( \pm2194803520 ; 0); 
( \pm389293216 ; 0); 
( \pm2672185425 ; 0); 
( \pm9857846460 ; 0); 
( \pm1293126240 ; 0); 
( \pm17699891040 ; 0); 
( \pm14408546880 ; 0); 
( \pm3007524114 ; 0); 
( \pm3402061572 ; 0)\}
$
(Figure~\ref{48_symm.png}),
